---
title: "Belief Analysis"
author: "Andrei Semenov and Annelise Pesch"
date: "August 15, 2017"
output:
  html_document: default
  pdf_document: default
---

```{r, echo = FALSE, warning = FALSE, message = FALSE}
#load libraries:
library(ggplot2) 
library(tidyr)
library(foreign)
library(doBy)
library(dplyr) 
library(reshape2)
library(PMCMR)
library(fifer)
library(psych)
library(pwr)
library(Hmisc)
library(sm)
library(sjmisc)
library(sjPlot)
library(readr)
library(xtable)

#load data 

#Cleaned data (already recoded and scaled variables)
#belief.csv

#Old data file: on Gdrive, beliEF Data _Final.csv

belief <- read_csv("~/BeliefStudy/belief.csv")

######################
#Variable Explanation#
######################

#Subject: Participant ID
#AgeMonths: Age in Months 1 decimal place
#Age: Age in Year
#Gender: 0 - Female 1 - Male
#Experimenter: 0 - Annelise 1- Andrei
#Task Order: Counterbalaned Task Order 1:8 Task Order followed the following format: [Theory of Mind (C/L):: Working Memory]
##################################
#####Working Memory Variables#####
#####F: forward              #####
#####B: backword             #####
#####Measures: Corsi & Word Span##
##################################
#Fwordraw: Raw "score" for forward word span (total number of correct trials across spans. Getting 1st span in a trial correct counts for all trials correct
#BWordRaw: Raw score for backword word span
#FWordSPan: Highest span length passed Forward
#BWordSpan: Highest span length passed backward
#FCorsihlp: Forward Corsi Highest Level Passed 1:9
#BCorsihlp: Backward Corsi Highest Level Passed 1:9
#FCorsiCal: Corsi Scored by performance under load. Corsi task featured 2 blocks of potential trials for each span length if participants #got the first span length correct, they moved on to the next one, if they failed they got 1 extra "chance" before failing. After failing #twice on a given span length, participants moved on to next block of forward corsi.
###FCorsi Cal takes (highest span - # of repeated trials under capacity)*highest span
#BCorsiCal: Same as FCorsi Cal but for backwards Corsi
#zFCorsi: Z-scored FCorsi Cal
#zBCorsi: Z-Scored BCorsi Cal
#zBWord: Z-Scored Backwards word Span Score (total items correct, if first item is correct, credit is given for subsequent items of that #span)
#zFWord: Same as zBWord but forwards
#zFCorsihlp: Z-Scored Forward Corsi highest level passed across both blocks
#zBCorsihlp: same as zFCorsihlp but backwards
#zFWordSpan: Z-Scored Forward Word highest Span length acheived
#zBWordSpan: Z-Scored Backward Word highest Span length acheived
#FWDcompositehlp: composite score of highest level passed: (zFcorsihlp + zFWordSpan)/2
#BWDcompositehlp: composite score of highest level passed: (zBcorsihlp + zBWordSpan)/2
##################################
#####Theory of Mind Variables#####
#####TB: True Belief         #####
#####FB: False Belief        #####
#####PAR: Perceptual Access  #####
#####L: Location             #####
#####C: Contents             #####
#####2/3/4: # of L/C         #####
##################################
#TBLTest: Outcome variable for True Belief Location: Derived from:
#     TBLTest<- ifelse((TBLCQ<=2), NA, 
        #ifelse((belief$TB2_Loc_Test==1), 1,
        #ifelse((belief$TB2_Loc_Test==0), 0, NA)))
# If participants answer control question incorrectly (CQ) then exclude them with NA There are 3 control questions, their sum is criteria
# 1 is pass, 0 is fail 
#TBCTest: Outcome variable for True Belief Contesnts:
#TBCTest<- ifelse((TBCCQ<=2), NA, 
#    ifelse((belief$TB2_Cont_Test==1), 1,
#    ifelse((belief$TB2_Cont_Test==0), 0, NA)))
#FB2LTest: These all follow the same format, checking control questions, if it's anything less than full credit, 0 or NA, passing is a 1
#PARM1: Perceptual Access Method 1: <Finish>
#PARM2C PAR method 2 Contents:
###RR = Score 1 on TB and 0 on FB
###PAR = Score 0 on TB and 1 on FB
###BR = Score 1 on TB and 1 on FB
###NA = NA in any task used to calculate PARM2C
#PARM2CF: Named version of PARM2C
#PARM2L: Same as PARM2C but for location
#PARM2LF: Named version of PARM2L
#FB3_LOC_NR: Non reality resposne for False belief 3 contents task
# Belief Response: 1
# Irrelevant Response: 0
# Reality Resposne: NA (because this variable is specifically for responses to non-reality variables)
#FB4_Cont_NR etc. same as FB3_LOC_NR
#ToMCompposite: Composite of ALL ToM Tasks:
# ToMComposite = belief$TB2_Loc_Test + belief$TB2_Cont_Test + belief$FB2_Loc_Test + belief$FB2_Cont_Test + belief$FB3_Cont_Comp + #belief$FB3_Loc_Comp + belief$FB4_Cont_Comp + belief$FB4_Loc_Comp
#ToMCompositeL: ToM Location Composite
#ToMCompositeC: ToM Contents Composite
#TBComp: True Belief Composite
```
#Data Analysis
##Data Prep
```{r, echo=FALSE, warning = FALSE, cache = TRUE}
###Preparing and re-classing data###

#Create Age Factors for 4-year-olds and 5-year-olds
#Create factor for gender
#Create factor for subject
#Create factor for experimenter
#Create factor for task order

belief$Age = factor(belief$Age,
                              labels = c("4", 
                                         "5"))
belief$Gender <- factor(belief$Gender)
belief$Subject <- factor(belief$Subject)
belief$Experimenter <- factor(belief$Experimenter)
belief$TaskOrder <- factor(belief$TaskOrder)

#Factor PAR Methods

belief$PARM2CF = factor(belief$PARM2C,
                     labels = c("RR", 
                                "BR", 
                                "PAR"))
belief$PARM2LF = factor(belief$PARM2L,
                     labels = c("RR", 
                                "BR", 
                                "PAR"))

View(belief)
```
##Descriptives

Participants: 85

Mean Age (in Months): 60.5 (43 4-year-olds, 42 5-year-olds)

Gender: Males: 38    Females: 47

```{r, echo = FALSE, fig.width = 6, fig.height = 6, cache = TRUE}
#Look for systematic group differences in gender/age/experimenter/task order

#differences in composites
#Age v. ToMComposites
sjp.xtab(belief$ToMCompositeC, belief$Age, show.total = FALSE)
sjp.xtab(belief$ToMCompositeL, belief$Age, show.total = FALSE)
sjp.xtab(belief$TBComp, belief$Age, show.total = FALSE)

lm.Age1<-lm(ToMCompositeC~Age, data = belief)
summary(lm.Age1) #Age significantly predicts differences P<.001 Beta = .95
lm.Age2<-lm(ToMCompositeL~Age, data = belief)
summary(lm.Age2) #Age significantly predicts differences P<.001 Beta = .83
lm.Age3<-lm(TBComp~Age, data = belief)
summary(lm.Age3) #Age is marginally significant P = .08 Beta = .3

#Conclusion, age is a contributing factor to the performance on ToM tasks. 

#Gender v. ToMComposites
sjp.xtab(belief$ToMCompositeC, belief$Gender, show.total = FALSE)
sjp.xtab(belief$ToMCompositeL, belief$Gender, show.total = FALSE)
sjp.xtab(belief$TBComp, belief$Gender, show.total = FALSE)

lm.Gender1<-lm(ToMCompositeC~Gender, data = belief)
summary(lm.Gender1)
lm.Gender2<-lm(ToMCompositeL~Gender, data = belief)
summary(lm.Gender2)
lm.Gender3<-lm(TBComp~Gender, data = belief)
summary(lm.Gender3)
#Conclusion, there are no systematic nor statistical differences in ToM tasks between the genders

#Experimenter v. ToMComposites
sjp.xtab(belief$ToMCompositeC, belief$Experimenter, show.total = FALSE)
sjp.xtab(belief$ToMCompositeL, belief$Experimenter, show.total = FALSE)
sjp.xtab(belief$TBComp, belief$Experimenter, show.total = FALSE)

lm.Exp1<-lm(ToMCompositeC~Experimenter, data = belief)
summary(lm.Exp1)
lm.Exp2<-lm(ToMCompositeL~Experimenter, data = belief)
summary(lm.Exp2)
lm.Exp3<-lm(TBComp~Experimenter, data = belief)
summary(lm.Exp3)
#Conclusion, there are no systematic nor statistical differences in ToM tasks between the two experimenters.

#differences in TB performance

#Age v. TB
sjp.xtab(belief$TBComp, belief$Age, show.total = FALSE)

#Gender v. TB
sjp.xtab(belief$TBComp, belief$Gender, show.total = FALSE)

#Experimenter v. TB
sjp.xtab(belief$TBComp, belief$Experimenter, show.total = FALSE)



```

## Group Differences building the model

###Group differences predicting ToM performance

There are differences between ages groups and their performance on ToM tasks: Age is included in future models.

```{r, echo = FALSE, cache = TRUE}
sjp.xtab(belief$ToMComposite, belief$Age, show.total = FALSE)
```

(8 is passing all ToM tasks, 0 is failing all TOM tasks)

We do not see similar patterns for gender or experimenter

There are differences between task order and ToM performanc: Task Order is included in future models.

###Group differences predicting working memory performance

```{r, echo = FALSE, cache = TRUE}

#differences in composites
#Age v. Corsi
sjp.xtab(belief$FCorsiCal, belief$Age, show.total = FALSE)
sjp.xtab(belief$BCorsiCal, belief$Age, show.total = FALSE)
sjp.xtab(belief$FCorsihlp, belief$Age, show.total = FALSE)
sjp.xtab(belief$BCorsihlp, belief$Age, show.total = FALSE)

lm.AgeWM1<-lm(FCorsiCal~Age, data = belief)
summary(lm.AgeWM1) #Age significantly predicts differences P<.001 Beta = 4.9
lm.AgeWM2<-lm(BCorsiCal~Age, data = belief)
summary(lm.AgeWM2) #Age significantly predicts differences P<.001 Beta = 4.4
lm.AgeWM3<-lm(FCorsihlp~Age, data = belief)
summary(lm.AgeWM3) #Age significantly predicts differences P <.001 Beta = .75 (span)
lm.AgeWM4<-lm(BCorsihlp~Age, data = belief)
summary(lm.AgeWM4) #Age significantly predicts differences P<.001 Beta = .84

#Conclusion, age is a contributing factor to the performance on Corsi Tasks. 

#Gender v. Corsi
sjp.xtab(belief$FCorsiCal, belief$Gender, show.total = FALSE)
sjp.xtab(belief$BCorsiCal, belief$Gender, show.total = FALSE)
sjp.xtab(belief$FCorsihlp, belief$Gender, show.total = FALSE)
sjp.xtab(belief$BCorsihlp, belief$Gender, show.total = FALSE)

lm.GenderWM1<-lm(FCorsiCal~Gender, data = belief)
summary(lm.GenderWM1) #No significant differences
lm.GenderWM2<-lm(BCorsiCal~Gender, data = belief)
summary(lm.GenderWM2) #No significant differences
lm.GenderWM3<-lm(FCorsihlp~Gender, data = belief)
summary(lm.GenderWM3) #No significant differences
lm.GenderWM4<-lm(BCorsihlp~Gender, data = belief)
summary(lm.GenderWM4) #No significant differences

#Conclusion, there are no systematic nor statistical differences in Corsi performance between the genders

#Experimenter v. Corsi
sjp.xtab(belief$FCorsiCal, belief$Experimenter, show.total = FALSE)
sjp.xtab(belief$BCorsiCal, belief$Experimenter, show.total = FALSE)
sjp.xtab(belief$FCorsihlp, belief$Experimenter, show.total = FALSE)
sjp.xtab(belief$BCorsihlp, belief$Experimenter, show.total = FALSE)

lm.ExpWM1<-lm(FCorsiCal~Experimenter, data = belief)
summary(lm.ExpWM1) #No significant Difference
lm.ExpWM2<-lm(BCorsiCal~Experimenter, data = belief)
summary(lm.ExpWM2) #No significant Difference
lm.ExpWM3<-lm(FCorsihlp~Experimenter, data = belief)
summary(lm.ExpWM3) #No significant Difference
lm.ExpWM4<-lm(BCorsihlp~Experimenter, data = belief)
summary(lm.ExpWM4) #No significant Difference

#Conclusion, there are no systematic nor statistical differences in ToM tasks between the two experimenters.


#Age v. Word Span
sjp.xtab(belief$FwordRaw, belief$Age, show.total = FALSE)
sjp.xtab(belief$FwordSpan, belief$Age, show.total = FALSE)
sjp.xtab(belief$BwordRaw, belief$Age, show.total = FALSE)
sjp.xtab(belief$BwordSpan, belief$Age, show.total = FALSE)

lm.AgeWM5<-lm(FwordRaw~Age, data = belief)
summary(lm.AgeWM5) #Age significantly predicts differences P<.05 Beta = 1.08
lm.AgeWM6<-lm(FwordSpan~Age, data = belief)
summary(lm.AgeWM6) #Age significantly predicts differences P<.001 Beta = .47
lm.AgeWM7<-lm(BwordRaw~Age, data = belief)
summary(lm.AgeWM7) #Age significantly predicts differences P <.01 Beta = 1.38
lm.AgeWM8<-lm(BwordSpan~Age, data = belief)
summary(lm.AgeWM8) #Age significantly predicts differences P<.05 Beta = .45

#Conclusion, age is a contributing factor to the performance on Corsi Tasks. 

#Gender v. Word Span
sjp.xtab(belief$FwordRaw, belief$Gender, show.total = FALSE)
sjp.xtab(belief$FwordSpan, belief$Gender, show.total = FALSE)
sjp.xtab(belief$BwordRaw, belief$Gender, show.total = FALSE)
sjp.xtab(belief$BwordSpan, belief$Gender, show.total = FALSE)

lm.GenderWM5<-lm(FwordRaw~Gender, data = belief)
summary(lm.GenderWM5) #No significant differences
lm.GenderWM6<-lm(FwordSpan~Gender, data = belief)
summary(lm.GenderWM6) #No significant differences
lm.GenderWM7<-lm(BwordRaw~Gender, data = belief)
summary(lm.GenderWM7) #No significant differences
lm.GenderWM8<-lm(BwordSpan~Gender, data = belief)
summary(lm.GenderWM8) #No significant differences

#Conclusion, there are no systematic nor statistical differences in Word Span performance between the genders

#Experimenter v. Word Span
sjp.xtab(belief$FwordRaw, belief$Experimenter, show.total = FALSE)
sjp.xtab(belief$FwordSpan, belief$Experimenter, show.total = FALSE)
sjp.xtab(belief$BwordRaw, belief$Experimenter, show.total = FALSE)
sjp.xtab(belief$BwordSpan, belief$Experimenter, show.total = FALSE)

lm.ExpWM5<-lm(FwordRaw~Experimenter, data = belief)
summary(lm.ExpWM5) #No significant Difference
lm.ExpWM6<-lm(FwordSpan~Experimenter, data = belief)
summary(lm.ExpWM6) #No significant Difference
lm.ExpWM7<-lm(BwordRaw~Experimenter, data = belief)
summary(lm.ExpWM7) #No significant Difference
lm.ExpWM8<-lm(BwordSpan~Experimenter, data = belief)
summary(lm.ExpWM8) #No significant Difference

lm.TO <-lm(FWDCompositehlp ~ TaskOrder, data = belief)
summary(lm.TO) #Significant (marginal) P=.06, beta = -.075
lm.TO2 <-lm(ToMCompositeC ~ TaskOrder, data = belief)
summary(lm.TO2) #Significant P <.05 beta = -.13
lm.TO3 <-lm(ToMCompositeL ~ TaskOrder, data = belief)
summary(lm.TO3) # Marginally significant at P<.071 Beta = 0.092
```

There are differences in working memory performance (in both Corsi block task and word span task) between task orders and age. There are no differences between gender or experimenter. 

##How are the measures correlated?
```{r, echo = FALSE, cache = TRUE}
########################################################################################
#WORKING MEMORY: 
########################################################################################
##Combine tasks for composite score (span)
belief$FWDcompositehlp = (belief$zFCorsihlp + belief$zFWordSpan)/2
belief$BWDcompositehlp = (belief$zBCorsihlp + belief$zBWordSpan)/2

#Combine scored variables for composite
belief$FWDcompositeScore = (belief$zFCorsi + belief$zFWord)/2
belief$BWDcompositeScore = (belief$zBCorsi + belief$zBWord)/2

#correlation table between working memory tasks

corr.tableWM = data.frame(
                  Age = c(belief$AgeMonths, na.rm=TRUE),
                  FCorsi = c(belief$zFCorsi, na.rm=TRUE),
                  BCorsi = c(belief$zBCorsi, na.rm=TRUE),
                  FCorsihlp = c(belief$zFCorsihlp, na.rm = TRUE),
                  BCorsihlp = c(belief$zBCorsihlp, na.rm = TRUE),
                  FwordSpan = c(belief$zFWordSpan, na.rm=TRUE),
                  BwordSpan = c(belief$zBWordSpan, na.rm=TRUE),
                  Fword = c(belief$zFWord, na.rm=TRUE),
                  Bword = c(belief$zBWord, na.rm=TRUE),
                  FWDcompositehlp = c(belief$FWDcompositehlp, na.rm=TRUE),
                  BWDcompositehlp = c(belief$BWDcompositehlp, na.rm=TRUE),
                  FWDcompositeScore = c(belief$FWDcompositeScore, na.rm = TRUE),
                  BWDcompositeScore = c(belief$BWDcompositeScore, na.rm = TRUE)
)
head(corr.tableWM)
rcorr(as.matrix(corr.tableWM), type = c("pearson"))

sjt.corr(corr.tableWM, "pairwise", "pearson")
sjp.corr(corr.tableWM, title = "Correlation between WM measures", corr.method = "pearson", na.deletion = "pairwise")


#belief$BWDcompositehlp = (belief$Z_Bcorsi_hlp + belief$Z_BwordSpan)/2
```


```{r, echo = FALSE}
#sjp.cor(corr.tableWM, title = "Correlation between WM measures", corr.method = "pearson", na.deletion = "pairwise")


```
 Correlation between WM is strong. Due to existing literature, backward counting tasks are a more reliable measure of WM. BWDcompositeSocre will be use. This is derived averaging zScores from backward corsi and backward word scores. 

##How does WM correlate with other measures?

```{r, echo = FALSE}
#z-score ToM outcome variables
belief$zToMC <- scale(belief$ToMCompositeC, center = TRUE, scale = TRUE)
belief$zToML <- scale(belief$ToMCompositeL, center = TRUE, scale = TRUE)
belief$zTB <- scale(belief$TBComp, center = TRUE, scale = TRUE)
head(belief)

corr.tableToMWM <- data.frame(
    Age = c(belief$AgeMonths, na.rm=TRUE),
    TaskOrder = c(belief$TaskOrder, na.rm = TRUE),
    BWDcompositehlp = c(belief$BWDcompositehlp, na.rm=TRUE),
    BWDcompositeScore = c(belief$BWDcompositeScore, na.rm = TRUE),
    ToMCompositeC = c(belief$ToMCompositeC, na.rm = TRUE),
    ToMCompositeL = c(belief$ToMCompositeL, na.rm = TRUE),
    TBComp = c(belief$TBComp, na.rm = TRUE),
    PARC = c(belief$PARM2C, na.rm = TRUE),
    PARL = c(belief$PARM2L, na.rm = TRUE),
    ToMC = c(belief$zToMC, na.rm = TRUE),
    ToML = c(belief$zToML, na.rm = TRUE),
    TB = c(belief$TBComp, na.rm = TRUE)
)
head(corr.tableToMWM)


#ToMCorr<-sjt.corr(corr.tableToMWM, "pairwise", "pearson")

#sjp.corr(corr.tableToMWM, title = "Correlation between WM measures and ToM measures", corr.method = "pearson", na.deletion = "pairwise")

```
`r sjt.corr(corr.tableToMWM, "pairwise", "pearson", no.output = TRUE)$knitr`

##Is there a difference in WM performance between belief, reality and PAR reasoners controlling for age, and task order?





   